Local to global N input modelling

### 2025-06-09 docs/manuscript.qmd
Fix citations

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(RColorBrewer)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

remove_unit("g_fish")
remove_unit("kg_fish")
remove_unit("t_fish")
install_unit("g_fish")
install_unit("kg_fish", "1000 g_fish")
install_unit("t_fish", "1000 kg_fish")
```

@@

```{r custom fuctions}
#| code-summary: Function to create sf polygons from bounding boxes

create_boxes <- function(box_list, label_positions, offset_deg) {
  boxes <- list()
  labels <- list()

  for(i in seq_along(box_list)) {
    name <- names(box_list)[i]
    coords <- box_list[[i]]
    pos <- label_positions[i]

    # Create polygon from bounding box coordinates
    box_coords <- matrix(c(
      coords[1], coords[3],  # lonmin, latmin
      coords[2], coords[3],  # lonmax, latmin  
      coords[2], coords[4],  # lonmax, latmax
      coords[1], coords[4],  # lonmin, latmax
      coords[1], coords[3]   # close polygon
    ), ncol = 2, byrow = TRUE)

    # Create sf polygon
    poly <- st_polygon(list(box_coords))
    boxes[[i]] <- st_sfc(poly, crs = 4326)

    # Calculate label position based on specification
    label_coords <- get_label_position(coords, pos, offset_deg[i])
    label_point <- st_point(c(label_coords[1], label_coords[2]))
    labels[[i]] <- st_sfc(label_point, crs = 4326)
  }

  # Combine into sf objects
  boxes_sf <- st_sf(
    name = names(box_list),
    letter = LETTERS[1:length(box_list)],
    geometry = do.call(c, boxes)
  )

  labels_sf <- st_sf(
    name = names(box_list), 
    letter = LETTERS[1:length(box_list)],
    geometry = do.call(c, labels)
  )

  return(list(boxes = boxes_sf, labels = labels_sf))
}

# Helper function to calculate label positions
get_label_position <- function(coords, position, offset) {
  lonmin <- coords[1]
  lonmax <- coords[2]
  latmin <- coords[3]
  latmax <- coords[4]

  # Parse position string
  parts <- strsplit(position, "_")[[1]]
  vertical <- parts[1]    # "top" or "bottom"
  horizontal <- parts[2]  # "left" or "right"
  location <- parts[3]    # "inside" or "outside"

  # Base coordinates for corners
  if(vertical == "bottom") {base_lat <- latmin} else {base_lat <- latmax}
  if(horizontal == "right") {base_lon <- lonmax} else {base_lon <- lonmin}

  # Apply offset for outside positioning
  if(location == "outside") {
    if(horizontal == "left") {base_lon <- base_lon-offset} else {base_lon <- base_lon+offset}
    if(vertical == "top") {base_lat <- base_lat + offset} else {base_lat <- base_lat - offset}
  }

  return(c(base_lon, base_lat))
}

lim_robin <- function(lons = c(144.0, 149.5), lats = c(-39.75, -44.00)) {
  coords <- data.frame(lon = lons, lat = lats) %>%
    st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
    st_transform(crs = "+proj=robin") %>% 
    st_coordinates()
  list(
    xlims = range(coords[, "X"]),
    ylims = range(coords[, "Y"])
  )
}

```

@@

| pk                   | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |

@@

| m                    | `r unname(params['m'])`          | -                        | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
| n                    | `r unname(params['n'])`          | -                        | Weight exponent for catabolism | @baldan_r_2018 |
| $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$\^{\circ}$C. Coefficient for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] | 

@@

| a                    | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| k                    | `r unname(params['k'])`          | -                        | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| eff                  | `r unname(params['eff'])`        | -                        | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 

@@

| mort                 | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |

@@

[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed?]{.aside}

@@

@@

All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
Major packages used include `terra` [@terra], `targets` [@targets], `future` [@future], `furrr` [@furrr], `renv` [@renv], and the `tidyverse` [@tidyverse].
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

# Supplementary stuff

@@

sens_data <- rbind(sens_weight, sens_excr) %>% 
  mutate(adj_param = factor(adj_param, levels = param_names$name))
```

Looking at @fig-param-sens-weight:

* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon. There must be more up-to-date measurements for Atlantic salmon in particular.

>>>>

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

remove_unit("g_fish")
remove_unit("kg_fish")
remove_unit("t_fish")
install_unit("g_fish")
install_unit("kg_fish", "1000 g_fish")
install_unit("t_fish", "1000 kg_fish")

packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate")

here("00_model_functions.R") %>% source()
```

@@

@@

| $p_k$                | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |

@@

| $m$                  | `r unname(params['m'])`          | -                        | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
| $n$                  | `r unname(params['n'])`          | -                        | Weight exponent for catabolism | @baldan_r_2018 |
| $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{\circ}$C. Coefficient for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] | 

@@

| $a$                  | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| $k$                  | `r unname(params['k'])`          | -                        | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| $eff$                | `r unname(params['eff'])`        | -                        | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 

@@

| $mort$               | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |

@@

[Plan to put full details of ingredients in a supplementary section. But possibly report these stats in Results under Uneaten feed?]{.aside}

@@

All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
Major packages used include `r cite_packages(packages)`.
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

@@

# Supplementary materials

@@

sens_data <- rbind(sens_weight, sens_excr)
```

The most sensitive parameter by far in @fig-param-sens-weight is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism). 
These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
